---
title: "WHO Health Data Analysis"
subtitle: "A Presentation by Marjella Ernst"
author: "Marjella Ernst"
date: "`r format(Sys.Date(), '%B %Y')`"

output:
  beamer_presentation:
    latex_engine: xelatex
    theme: "Berlin"
    colortheme: "dove"
    fonttheme: "structurebold"
    slide_level: 2
    toc: false
    keep_tex: true
    fig_caption: true
fontsize: 11pt
linestretch: 1.2
numbersections: true
link-citations: true
bibliography: Tex/ref.bib
csl: Tex/harvard-stellenbosch-university.csl
---



<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
library(dplyr)
library(broom)
library(knitr)
library(kableExtra)
library(pander)
library(memisc)
#install.packages("modelsummary")
#install.packages("flextable")
library(modelsummary)   # wraps broom + supports flextable
library(flextable)
library(ggplot2)

Health <- "data/Health/HealthCare.csv" %>% read.csv()
```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

This presentation explores the relationship of various factors such as:
- stress
- physical exercise
- sleep, and

on health.

# Hypotheses to test

1. sleeping is more important to health than exercise
2. living a stress free lifestyle has a major impact on health

# Research Question

"Which are the main influencing factors on health and how can we use these insights to improve it?"

# Data 

- The data used for this analysis originates from the **World Health Organization (WHO)**.
- It includes self-reported indicators on:
  - Physical activity
  - Sleep quality
  - Stress levels
  - Caloric intake

- The dataset builds the empirical basis for testing the relationship between lifestyle factors and health outcomes

# Methodology

- A multiple linear regression model is used to estimate the effect of:
  - **Exercise** (physical activity),
  - **Sleep quality**, and
  - **Stress level**
  
  on the dependent variable **Health** (approximated by excess caloric intake).


- The model is specified as:
\[
\text{Health}_i = \beta_0 + \beta_1 \cdot \text{Exercise}_i + \beta_2 \cdot \text{Sleep}_i + \beta_3 \cdot \text{Stress}_i + \varepsilon_i
\]

- In R, the model is estimated as:

```r
lm(Health ~ Exercise + Sleep + Stress, data = processed)
```

# Challenge: What is Health?

- For the purpose of this analysis, health is approximated by excess body weight
  - This serves as a proxy indicator due to data limitations
  - Other common indicators, such as BMI, are not available in the dataset


# Regression Results

```{r results='asis', echo=FALSE}
source("code/Process_Data.R")
process_data(Health)
```

## Interpretation of Results I

- **Exercise** has strong and highly significantly positive effect on health  
  - Coefficient: 285.77 (***), p < 0.001  
  - Interpretation: Higher physical activity is strongly associated with better health (less excess weight)

- **Sleep** shows small positive effect, but is not statistically significant
  - Coefficient: 30.22, p > 0.1  
  - No strong evidence that sleep quality alone explains variation in health

## Interpretation of Results II

- **Stress** has a small negative effect, but is also not statistically significant
  - Coefficient: –5.36, p > 0.5  
  - Cannot conclude that stress significantly affects health in this model

- **Model fit**:
  - R² = 0.652 → model explains ~65% of the variation in health
  - Adjusted R² = 0.642 is still high after adjusting for model complexity 
  - AIC = 1370.7 model complexity vs. fit trade-off

# Limitations

- Health is difficult to measure because it includes multiple dimensions:
  - Physical aspects (e.g., number of illnesses, fitness)
  - Mental aspects (e.g., stress resistance, absence of psychological conditions)

- Many influencing factors of health are themselves difficult to observe or quantify:
  - Genetics, sleep, nutrition
  - Environmental and external factors
  - Access to health care

- There is a significant risk of reverse causality:
  - Poor health can increase stress
  - Illness may limit exercise
  - Health problems can disrupt sleep

# Conclusion

- Exercise is found to be clearly statistically significant for health

- Sleep and stress show expected effects but lack statistical significance  

- The model explains a large share of variation in health (~65%)  

- Hower, health is a multifaceted concept, more complex than this model can explain 

- Further research should include:
  - Better proxies for health (e.g., BMI, blood pressure, clinical diagnoses)
  - Longitudinal data to address reverse causality
  - Interaction effects (like stress and sleep)




