---
# IMPORTANT: Change settings here, but DO NOT change the spacing AT ALL.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Insights into Streaming Consumer Preferences"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Some Guy}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Marjella Ernst"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Stellenbosch University, Stellenbosch, South Africa" # First Author's Affiliation
Email1: "29835569\\@sun.ac.za" # First Author's Email address

# Comment out below to remove both. JEL Codes only given if keywords also given.

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
#abstract: |
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction 

In times of declining Netflix audiences and increasing production costs, it is more important than ever to understand what audiences really want. This brief document analyses Netflix data up to 2023, as well as data from the Internet Movie Database to understand which genres audiences from different parts of the world value. This analysis includes natural language processing to analyse sentiment of text-based movie ratings. The results of the sentiment analysis are then plotted against movie ratings, to show whether the sentiment of ratings correlates with the ratings assigned.

```{r}
library(dplyr)
library(tidyr)
library(stringr)
library(tidytext)
library(scales)
library(ggplot2)
library(ggrepel)
```

```{r}
Titles <- readRDS("data/netflix/titles.rds")
Credits <- readRDS("data/netflix/credits.rds")
Movie_Info <- read.csv("data/netflix/netflix_movies.csv")
```

```{r}
source("code/Merge_Df.R")
merge_df(Titles, Movie_Info)
```

# Analysis Results

The following section briefly discusses results of the film and series analysis.

## Length Development

In times of shorter concentration span through social media usage, screening time is known to be a decisive factor in determining a movie's success. Hence, the average length of movies and series has been analysed over time. It becomes visible that time has declined especially after 2005, supporting the hypothesis of reduced concentration span of viewers. It is therefore advisable to offer shorter over longer movies on the platform. 


```{r}
region_data <- readRDS("results/region_data.rds")
source("code/Length_Development.R")
length_development(region_data)
```

## Genre Popularity by Region

In a next step, genre popularity by region was analysed to gain an overview which movies should be offered to which audience group. The insights can be used to tailor the offering of the new platform to users preferences in order to optimize the market fit of the product. 


```{r}
source("code/Sentiment_Analysis.R")
sentiment_analysis(region_data)
```


```{r}
data_sentiment <- readRDS("results/data_sentiment.rds")
source("code/Genre_Region_Summary.R")
genre_region_summary(data_sentiment)
```


## Sentiment vs. Rating Analysis

Lastly, it has been analysed whether sentiment of ratings written on online platforms aligns with actual ratings assigned. The results suggest that sentiment of ratings tends to be more negative than overall user ratings. This gives the impression, that ratings overall are written more critically, than overall ratings assigned.  

```{r}
top_genres <- readRDS("results/top_genres.rds")
source("code/scatterplot_sentiment_rating.R")
scatterplot <- plot_sentiment_vs_rating(top_genres)
print(scatterplot)
ggsave("results/plot_sentiment_vs_rating.png", plot = scatterplot, width = 6, height = 5, dpi = 300)

```

# Conclusion

The analysis suggests that offerings on the new platform should be rather short. In addition, the genre preference matrix gives insights which genres to focus on per region. Following these insights, the new platform will ensure that the audiences demands are met, such that offerings have a higher possibility of being successes.








