---
# IMPORTANT: Change settings here, but DO NOT change the spacing AT ALL.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Billionaire Analysis"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Some Guy}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Marjella Ernst"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Stellenbosch University, Stellenbosch, South Africa" # First Author's Affiliation
Email1: "29835569\\@sun.ac.za" # First Author's Email address


# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
library(dplyr)
library(ggplot2)

```


```{r}
Billions <- read.csv("data/Billions/billionaires.csv")
```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

This report analyses data on billionaires to test three hypotheses:

1. **Hypothesis 1:** The United States has a higher number of self-made billionaires—those who did not inherit their wealth—compared to other (non-U.S.) regions.

2. **Hypothesis 2:** Among self-made billionaires, the share who accumulated wealth by founding businesses in the consumer services sector has declined over time, while the share in the technology sector has increased.

3. **Hypothesis 3:** There is a positive relationship between a country's GDP and the level of innovation in the consumer services sector.

\newpage

# Billionaire Analysis

## Share of Selfmade Billionaires per Region

To analyse whether the first statement is true, the share of US-based self-made billionaires is plotted against the share of non-US-based self-made billionaires (here called Emerging Economies). The results show that the hypothesis is true: the US has more self-made billionaires than other countries.

```{r}
source("code/Selfmade_Analysis.R")
selfmade_analysis(Billions)
selfmade_share <- readRDS("results/selfmade_share.rds")
source("code/Selfmade_Visualization.R")
selfmade_visualization(selfmade_share)
```
\newpage

## Industry Shares

Next we test the second hypothesis, that the share of self-made billionaires that got rich by founding businesses in consumer services has declined, while the share of technology self-made billionaires has increased. The data is being grouped by industries and an industry share by year is being calculated. The labels on the graph are a bit deterred, but the results suggest that the second hypothesis is not entirely true. The share of overall billionaires in consumer services has first increased and then reduced, remaining on a similar level in 2014 as in 1996. The share of tech billionaires follows a similar pattern. 

```{r}
analysis <- readRDS("results/analysis.rds")
source("code/Industry_Trends.R")
industry_trends(analysis)
```
\newpage

## Correlation

To test the third hypothesis that richer countries provide more innovation in consumer services, a correlation is carried out.
The results suggest that there is indeed a positive relationship between (logged) GDP and the share of innovations in the consumer industry.


```{r}
source("code/Correlation_Analysis.R")
correlation_analysis(analysis)
```

# Conclusion

In summary, hypothesis one and three were prooved correct, while hypothesis two was rejected.